SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-06 results.tex
Updated IPC Speedup numbers
...to reflect the final configuration

PPF yields a geometric mean speedup of \textbf{27\%} over the baseline. 
This is equivalent to \textbf{4.63\%} over DA-AMPM, \textbf{4.61\%} over BOP 
and \textbf{3.78\%} over SPP. Out of the 95 simpoints developed for SPEC 
CPU 2017, PPF nearly matches or outperforms most of the prefetchers on 91 
simpoints. PPF fails to match the improvement offered by BOP only for 
{\tt 607.cactuBSSN\_s} and {\tt 654.roms\_s} traces.

@@

\noindent \textbf{4-CORE ENVIRONMENT}
\newline
Figure~\ref{Fig:4Core_SPEC2017} shows a comparison of speedups obtained on
4-core mixes of a memory intensive subset SPEC CPU 2017. We plot all 4
prefetchers, normalized to the baseline. The workloads have been sorted in
increasing order of the speedup. PPF offers a speedup of \textbf{51.7\%} on
these traces, and improvement of \textbf{11.9\%} over the baseline SPP,
\textbf{10.2\%} over the next DA-AMPM, and \textbf{17.4\%} over BOP.

On a different set of fully random SPEC CPU 2017 4-core mixes (not illustrated
for space reasons), PPF provides an IPC speedup of \textbf{26.2}\% over the
baseline, which is an improvement of \textbf{5.7}\% over SPP.

@@

\noindent \textbf{8-CORE ENVIRONMENT}
\newline
The sorted comparison of speedups on the memory intensive 8-core mixes is
shown in Figure~\ref{Fig:8Core_SPEC2017}. PPF improves baseline performance
by \textbf{38.6\%}, an improvement of \textbf{10.7\%} over SPP. For a random
set of SPEC CPU 2017 mixes (not illustrated for space reasons), PPF improves
performance by \textbf{23.6\%} over the baseline, corresponding to
\textbf{4.8\%} over SPP. This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.

@@

For 4-core memory intensive mixes, PPF improves the baseline by
\textbf{59.2\%}, \textbf{8.7\%} ahead of SPP. For 8-core memory intensive
mixes, the speedup over the baseline is \textbf{47.9\%}, \textbf{11.5\%} ahead
of SPP.

Figure~\ref{Fig:CloudSuite} shows the performance benefit comparison of all
the prefetch schemes on 4 different applications in the CloudSuite benchmark.
In general, these applications are prefetch agnostic. Even so, PPF manages a
\textbf{3.7\%} improvement over no prefetching, putting it ahead of the next
best prefetcher, SPP, which provides a 3.08\% speedup.

>>>>

PPF yields a geometric mean speedup of \textbf{26.95\%} over the baseline. 
This is equivalent to \textbf{4.63\%} over DA-AMPM, \textbf{4.61\%} over BOP 
and \textbf{3.78\%} over SPP. Out of the 95 simpoints developed for SPEC 
CPU 2017, PPF nearly matches or outperforms most of the prefetchers on 91 
simpoints. PPF fails to match the improvement offered by BOP only for 
{\tt 607.cactuBSSN\_s} and {\tt 654.roms\_s} traces.

@@

\noindent \textbf{4-CORE ENVIRONMENT}
\newline
Figure~\ref{Fig:4Core_SPEC2017} shows a comparison of speedups obtained on
4-core mixes of a memory intensive subset SPEC CPU 2017. We plot all 4
prefetchers, normalized to the baseline. The workloads have been sorted in
increasing order of the speedup. PPF offers a speedup of \textbf{51.2\%} on
these traces, and improvement of \textbf{11.4\%} over the baseline SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.

On a different set of fully random SPEC CPU 2017 4-core mixes (not illustrated
for space reasons), PPF provides an IPC speedup of \textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.

@@

\noindent \textbf{8-CORE ENVIRONMENT}
\newline
The sorted comparison of speedups on the memory intensive 8-core mixes is
shown in Figure~\ref{Fig:8Core_SPEC2017}. PPF improves baseline performance
by \textbf{37.6\%}, an improvement of \textbf{9.7\%} over SPP. For a random
set of SPEC CPU 2017 mixes (not illustrated for space reasons), PPF improves
performance by \textbf{23.4\%} over the baseline, corresponding to
\textbf{4.6\%} over SPP. This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.

@@

For 4-core memory intensive mixes, PPF improves the baseline by
\textbf{59.1\%}, \textbf{8.6\%} ahead of SPP. For 8-core memory intensive
mixes, the speedup over the baseline is \textbf{47.8\%}, \textbf{11.3\%} ahead
of SPP.

Figure~\ref{Fig:CloudSuite} shows the performance benefit comparison of all
the prefetch schemes on 4 different applications in the CloudSuite benchmark.
In general, these applications are prefetch agnostic. Even so, PPF manages a
\textbf{3.78\%} improvement over no prefetching, putting it ahead of the next
best prefetcher, SPP, which provides a 3.08\% speedup.
